Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-07 text/paper/paper1.tex
discussion sec com

@@

In sum, if the interpretation of our data as suggested here is correct
(we will argue presently that it is), then both traditionalism and
grammaticalism are in need of revision. Traditionalism must explain
the availability of local readings, grammaticalism must revise its
selection criterion among readings.

>>>>

\subsection{Interpretation}
\label{sec:interpretation}

@@

In sum, if the interpretation of our data as suggested here is
correct, then both traditionalism and grammaticalism are in need of
revision. Traditionalism must explain the availability of local
readings, grammaticalism must revise its selection criterion among
readings. In the remainder of this section we would like to discuss
whether this interpretation of our data is feasible.

Several worries and objections are conceivable that might cast doubt
on the previous interpretation of our experimental data. In the
following we would like to address some of these that we consider most
pressing. Eventually, however, we conclude that the main point raised
above remains valid: neither traditionalism, nor grammaticalism
explains the observations even under alternative interpretations of the
data.

There are many ways in which it could be questioned whether our design
really reliably indicates the preference relation in
(\ref{bsp:observed-preferences}) among readings of our target
sentences. A first potential worry from that class that can be
dismissed rather quickly is that the incremental verification task
(\ivt) might simply select for the weakest possible reading. This idea
might be grounded in the observation that the preferred \lc-readings
of our target-related controls entail the dispreferred
\ec-readings. It could thus be argued that the difference in responses
for preference-related controls are due to the entailment properties,
not the known preference relation over \lc- and \ec-readings. But this
does not explain why the distribution of responses in the target
conditions are obviously not governed by logical strength. In fact, it
is a very noteworthy point that although entailment relations among
readings differ between \as- and \es-sentences, the observed response
pattern does not. (This is what is at the heart of the problem for a
grammaticalism that relies on the strongest meaning hypothesis.)

But maybe, a similar kind of objection goes, it is not feasible to
actually compare results from the preference-related controls to
results from our target conditions, because the kind of ``ambiguity''
is of a different kind. In the former we have a case of syntactic
ambiguity, in the latter a small number of competing pragmatic
enrichments. The former is a case of perceived ambiguity (some of our
subjects reported this in the
\emph{Nachbefragungsbogen}\dn{English?}), the latter arguably is
not \citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps
even if the distribution of responses is indicative of the known
preference patterns in preference-related controls, this would not
necessarily mean that the distribution of responses in target
conditions is indicative of preference relations.

There are two kinds of reply to this objection (and others like
it). The first kind of reply starts with a concession. It is true that
we cannot conclude with certainty that our data implies that
(\ref{bsp:observed-preferences}) is the actual preference relation
among candidate readings of our target sentences. But we do not have
to either. Maybe in fact, the observed distribution has nothing to do
with preferences over readings. It does not matter. The main point is
that neither traditionalism nor grammaticalism predicts the observed
distribution of responses. The second kind of reply is fatalistic but
stubborn. If we assume that the \ivt is incapable of indicating
preferences among readings for pragmatically unspecified, then it
should at least be able to indicate availability of readings, should
it not? And if we deny the observed response patterns the power to
indicate preference, what should the information about availability of
readings be that we may safely infer from it? It should be that local
readings are available and that global readings are not. But that is
again bad news for both traditionalism and grammaticalism. The former
cannot explain the substantial number of local responses, the latter
doesn't explain the absence of global responses.

\begin{itemize}
\item different kinds of ``multiple readings'': syntactic ambiguity
  vs.~pragmatic xxx
\item typicality after all
\end{itemize}
